---
geo---
title: Tag Label
format: html
editor: visual
---

```{r, setup}

id <- "91D"

knitr::opts_knit$set(root.dir = normalizePath(".."))
library(GeoPressureR)
library(ggplot2)
```

## Sensor data and crop date

```{r tag_create}
tag <- tag_create(config::get("id", id),
  crop_start = config::get("crop_start", id),
  crop_end = config::get("crop_end", id)
)
```

## Run [simple labelling checks](https://raphaelnussbaumer.com/GeoPressureManual/labelling-tracks.html#simple-checks)

**Check 1**

```{r}
tag <- tag_label(tag)
```

**Check 2**

```{r}
plot(tag, type = "pressure")
```

## Run [Pressurepath checks](https://raphaelnussbaumer.com/GeoPressureManual/labelling-tracks.html#pressurepath-checks)

Compute pressure map on a coarse grid to perform checks 3-5.

```{r}
# stap2duration(tag$stap, return_numeric = F)
tag <- tag_set_map(tag,
  extent = config::get("extent", id),
  scale = 5,
  include_min_duration = 0
) |>
  geopressure_map(max_sample = 250)
```

```{r}
path = tag2path(tag, interp=2)
plot(tag, path = path)
```

**GeoPressureViz**

```{r}
path <- geopressureviz(tag, path)
```

**Pressurepath**

```{r}
pressurepath <- pressurepath_create(pressurepath)
```

**Check 3**

```{r}
plot_pressurepath(pressurepath)
```

**Check 4**

```{r}
plot_pressurepath(pressurepath, type = "hist")
```

## Run [GeoPressureViz checks](https://raphaelnussbaumer.com/GeoPressureManual/labelling-tracks.html#geopressureviz-checks)

```{r}
geopressureviz(
  tag,
  path = pressurepath,
  # path = most_likely_path,
  # marginal = marginal
)
```

## Update of `tag` and `pressurepath`

::: callout-tip
*Delete this block when you have read!*

You can use `tag_upate()` and `pressurepath_update()` every time you edit and export a new label file from Trainset. You might want to start from a new tag and pressurepath variable if you encounter any problem.
:::

```{r}
tag <- tag_update(tag)
```

```{r}
pressurepath <- pressurepath_update(pressurepath, tag)
```
